---
title: "RED & MRI ID Check"
author: "Stepheni Uh"
date: "December 7, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Libraries
```{r, include=FALSE}
#load libraries
libs <- c('ggplot2', 'tidyverse', 'stringr', 'psych', 
          'stats', 'ggpubr', 'factoextra', 'kohonen', 'gridExtra',
          'readxl', 'aod', 'rstatix', 'ez', 'ggpubr', 'reshape2', 'afex', 'emmeans')
lapply(libs, require, character.only = T)
```

Aim of this script:
- Check to make sure new sub-ids and old sub-ids are correctly matched with participants
- Pull in IDs from newly created csv and old files

This is especially needed when we create the events file for each subject for new first level and group analyses

###########################################

Read in CSVs with appropriate IDs
```{r, include=FALSE}
new_ids <- read.csv("X:/RED/RED_subcbu_ids.csv", stringsAsFactors = FALSE)

# old data
old_ids_data <- read_excel("C:/Users/su01/ownCloud/PhD/RED/Go-NoGo data/RED_MRI_nopid.xlsx", sheet = "final sample")

# select old IDs only from data
old_ids <- old_ids_data %>% select(sub_id_3digit, mri_id, red_id)

# old data that has all the info
old_ids_all <- read_excel("C:/Users/su01/ownCloud/PhD/RED/Go-NoGo data/RED_MRI_nopid.xlsx", sheet = "task")
```

Rearrange the old IDs because these are organized in non-bids form
```{r}

# first select ids that have a sub_id value
old_ids_all <- old_ids_all %>% filter(!is.na(sub_id))

# select the first three columns only first
old_ids_selected <- old_ids_all %>% select(sub_id, mri_id, red_id)

# split up the IDs by sub - this is a weird way to go about it but it works
ids_old <- as.data.frame(str_split_fixed(old_ids_selected$sub_id, "sub", 2), stringsAsFactors = FALSE)
# sub disappears so add that plus the -0 into the first column
ids_old$V1 <- "sub-0"
# concatenate V1 & V2 to get new sub_ids
ids_old$sub_id <- paste0(ids_old$V1,ids_old$V2)

# add this column into old dataset that we will use to merge
old_ids_selected <- cbind(old_ids_selected, ids_old$sub_id)

# rearrange columns and rename the ids_old$sub_id (drop the original sub_id column)
old_ids_selected <- old_ids_selected %>% select(sub_id_old = `ids_old$sub_id`,
                                                mri_id,
                                                red_id)

# make sub_id as character (turns into factor after binding)
old_ids_selected$sub_id_old <- as.character(old_ids_selected$sub_id)

# recode sub-028+F134 & sub-060 CBU_ID values
old_ids_selected$sub_id_old[old_ids_selected$sub_id_old == "sub-028+F134"] <- "sub-028"
old_ids_selected$mri_id[old_ids_selected$mri_id == "CBU190642??"] <- "CBU190642"

# order sub-ids alphabetically
old_ids_selected <- old_ids_selected[order(old_ids_selected$sub_id_old),]
```

Match the columns to make sure they are correct
```{r, include = FALSE}
# recognize that old ids we are missing 5 but you can check in this the "task" sheet of old excel file that was read in

# put old sub_ids into a list to filter out the ones not included in the new dataset
oldids <- old_ids_selected$sub_id

# filter out ids not in the old list
new_ids_selected <- new_ids[new_ids$sub_id %in% oldids,]
# separate values since old ones don't have the MRI tag
new_ids_selected <- new_ids_selected %>% separate(cbu_id, c("cbu_id", "mri_tag"))

# merge to check the two columns of each one
test <- merge(new_ids_selected, old_ids_selected, by=1:2)

# create new dataset
check <- cbind(new_ids_selected, old_ids_selected)
check$match_subids <- check$sub_id == check$sub_id_old
check$match_cbuids <- check$cbu_id == check$mri_id

# create CSV file for check purposes in imaging RED folder
write.csv(check, "X:/RED/RED_bids_cbu_ids.csv")

```

